Oasis or Mirage? \\ Trade Network Propagation of Deforestation

### 2024-01-04 paper/main.tex
add figs for competitors

\begin{abstract}
    Log production is destroying forests around the world and contributing to global warming. To address deforestation, various countries have begun to adopt policies to restrict log exports. However, even if one country restricts log exports, the countries that have been importing logs may increase their log production to compensate for their previous imports. It is also possible that other countries will increase their log exports to the log consuming countries. In this case, one country's log export restrictions could induce deforestation in other countries through trade networks. In this paper, we focus on two policies, Russia's log export restrictions in 2007 and Myanmar's log export ban in 2014, to demonstrate how these policies affect the log industry in other countries through trade networks. We find that when one country restricts log exports, log production increases in their previously main export destination. This result suggests that through a network of trade, one country's pro-environmental policies can cause environmental damage in other countries.
\end{abstract}

@@

Using annual trade flow and production data of forestry industries, I employ shift-share design to empirically demonstrate effects of supply shock triggered by the ban of log exports. I regress outcome of each country on how much the country is exposed to the supply shock. The exposure to the shock is measured with interaction of two parts. The first part called ``shift'' is a measure of how much export-restricting country reduces their export to the rest of the world with the restriction. The second part called ``share'' is a measure of how much each country has been dependent on a specific market or industry before the restriction. Combining these two parts, we obtain measure of how much each country is exposed to the Russia or Myanmar's export restriction policy. By using this shift-share approach, I find that when log export restrictions are imposed in a country, log production increases in the country with the larger exposure to that supply shock, i.e., the country that was the export-restricting country's major export destination. This indicates that a country's log export restrictions contribute to deforestation in its major trading partners. On the other hand, for countries that exported to markets similar to that export-restricting country, there was no significant response in terms of production, export volume, or export value to the export-restriction shock. These results suggest that an pro-environmental policy in one country to protect its own forest has effect to propagate deforestation to their previous trade partners. This implicates that an efficacy of one country's forest protection can be crowded out by the spillover effects. It emphasizes that one government policy to protect its own forest is not sufficient to tackle with global environmental issue.\\

@@

This paper contributes to fill the gap between literature on deforestation and that on pollution heaven hypothesis by empirically shows trade network propagates deforestation with one country's regulation. This study will provide critical evidence in discussing how to solve the issue of deforestation. That is because it is necessary to globally maintain forests and increase how much carbon dioxide can be absorbed in a global scale when we tackle international environment issue such as climate change. Protection of forests in one country at the expense of another country's forest does not contribute to reduction in global carbon dioxide. The results of this paper emphasizes this important implication. \\

@@

In addition to FAOSTAT forestry data, I employ two other data sources. First, I use intra-country bilateral distance data to estimate the impact of distance on trade flows. The distance data are borrowed from the GeoDist database provided by the Centre d'Etudes Prospectives et d'Informations Internationales (CEPII). I use bilateral distance between centers of gravity weighted by the population of each country. Second, we use annual GDP data from the World Bank database. I provide descriptive evidence of this dataset in the next section.\\

@@

\subsection{Russia's log export restriction in 2007}
Russia developed the largest coniferous forest in the world, the Siberian ``taiga'', which accounted for half of the world's supply of coniferous wood.  To cope with the deforestation and to promote domestic wood processing industry, Russian government imposed an export tax of 6.5\% in July 2007, rising to 20\% on July 2007 and 25\% in April 2008 on logs exported from Russia. This restriction on log exports was introduced due to the Russian domestic situation. Additionally, as METI points out, the new Russian Forest Code, which was base of these export tax policies, was founded in December 2006. This haste of policy interventions supports our assumption that the policy was exogeneous shock for the rest of the world. \\

@@

\section{A Model of Deforestation Propagation}
Based on the properties of the roundwood trade network, this section constructs a simple model of the roundwood trade, and then presents a hypothesis induced by prediction of the model. The basic framework is quantity competition, what is called, Cournot competition. In usual Cournot setting, firms decide quantity of supply to a market to maximize their profit. This section describes the Cournot competition model as a game where $n$ countries supply homogeneous roundwood to one market. I introduce a general model at first, and then simplify the model to discuss the implication. \\

I would like to assume that there are n countries which has one market denoted by $M_i$, respectively. Thus, in total, there are $n$ markets $\{ M_1, ..., M_n \}$. In addition to the market, each country has one supplier firm $F_i$, and there are $n$ firms $\{ F_1, ..., F_n \}$ in total. Thus, this is a Cournot model where markets and firms belong to a bipartite graph. Every firm produces an homogeneous good to supply $n$ markets. Each firm choose a vector comsisted of quantity to supply each market, $\mathbf{q}_i = (q_{i1}, ..., q_{in})$ where $q_{ij}$ means quantity that firm $i$ supplies to market $j$. Every market has an identical inverse linear demand function $p_i = D(q_{1i}, ..., q_{ni}) = a_i - \sum_{j=1}^n q_{ji}$. Profit function of each firm is given by $\pi_i (\mathbf{q}_1, ..., \mathbf{q}_n) = \sum_{j = 1}^{n} ((a_j - \sum_{k=1}^n q_{kj}) q_{ij} - c_{i} (\sum_{j = 1}^{n} q_{ij} ) ^ 2 )$. Firms choose their strategy $\mathbf{q}_i$, that is, how much the firm produce and supply to each market, to maximize their profit. As \cite{bimpikis2019cournot} discusses, there is unique Nash equilibrium when this game has symmetric structure, that is, $a_1 = a_2 = ... = a_n = a$ and $c_1 = c_2 = ... = c_n = c$. On the other hand, the uniqueness of the equilibrium and the analytical solution is unknown for assymmetric cases. However, our interest is how assymmetric case where each firm has heterogeneous trade cost to the markets. To be more precise, I would like to discuss how assymmetric trade costs affect firms' decision when one of the firm exit from the markets. Therefore, we need to simplify this model from the general model. \\

From now on, we will consider a case where there are three countries. We assume that one of the three countries (country $1$) has both a market and a supplier, and the other two countries (country $2$ and country $3$) have only a supplier respectively. We can consider the country with both a market and a supplier as a country which produce roundwood and supply to Chinese market itself. On the other hand, the rest countries are developing countries that have plenty of forests to supply to the large country but that do not have a sufficiently large domestic market, such as Myanmar. Each of the three suppliers (Supplier $i$) chooses quantity $q_i$ to supply the market. The market of country $1$ has a inverse linear demand function
\begin{align}
    p = a - \sum_{i=1}^3 q_i
\end{align}

@@

Thus, we obtain 
\begin{align}
    q_1^* = \frac{4 a c_{2} c_{3} + 2 a c_{2} + 2 a c_{3} + a}{8 c_{1} c_{2} c_{3} + 8 c_{1} c_{2} + 8 c_{1} c_{3} + 6 c_{1} + 8 c_{2} c_{3} + 6 c_{2} + 6 c_{3} + 4} \\
    q_2^* = \frac{4 a c_{1} c_{3} + 2 a c_{1} + 2 a c_{3} + a}{8 c_{1} c_{2} c_{3} + 8 c_{1} c_{2} + 8 c_{1} c_{3} + 6 c_{1} + 8 c_{2} c_{3} + 6 c_{2} + 6 c_{3} + 4} \\
    q_3^* = \frac{4 a c_{1} c_{2} + 2 a c_{1} + 2 a c_{2} + a}{8 c_{1} c_{2} c_{3} + 8 c_{1} c_{2} + 8 c_{1} c_{3} + 6 c_{1} + 8 c_{2} c_{3} + 6 c_{2} + 6 c_{3} + 4}
\end{align}

@@

Finally, we would like to check how assymmetric trade cost affects each firm's equilibrium strategy (while assuming that production cost is identical among suppliers). As we can infer obviously from the equilibrium strategies, $c_i > c_j > c_k$ implies $q_i^* < q_j^* < q_k^*$ before one firm exits from the market and $c_i > c_j$ implies $q_i^{**} < q_j^{**}$ after one firm exits from the market. It implies that suppliers who need to pay large shipping cost to supply the market produce relatively small quantity. Our main interest is how different trade cost affects suppliers' reaction to the other supplier's exit. The difference in equilibrium supply quantity between before and after Country $3$'s export ban is given by:

@@

Intuitively speaking, we expect that $\Delta_i > \Delta_j$ if $c_i < c_j$. Since the form of equilibrium strategies is too complicated to analytical proove this intuitive relationship, I presents results of analytical simulation which support this intuitive property. Figure \ref{fig:cournot_simulation} displays simulation results where $a = 10$ (the intercept of the inverse demand function is $10$) and $c_3 = 1$ (supplier $3$'s cost to produce and supply $q_3$ units is $1$). I calculate $\Delta_1$ and $\Delta_2$ for a total of 121 combinations of $c_1 = 0, 1, ..., 10$ and $c_2 = 0, 1, ..., 10$. Each dot in the figure shows the magnitude relationship between $\Delta_1$ and $\Delta_2$ with its shape and the difference with its color. This figure implies that $\Delta_1 > \Delta_2$ if $c_2 > c_1$, that $\Delta_1 = \Delta_2$ if $c_2 = c_1$, and that that $\Delta_1 < \Delta_2$ if $c_2 < c_1$. In addition to this simulation, I confirm that this result is not sensitive to the value of $a$ and $c_3$. These results support the property of ``$\Delta_i > \Delta_j$ if $c_i < c_j$ ''. \\

@@

Moreover, this property suggests that if supply shock happens to one market, then the supplier with the smallest transportation costs will increase its production and its supply to the market to the greatest extent. In other words, the suppliers located in the same country as the market will increase their production and supply by larger extent than the foreign suppliers. For example, if China, who imported a lot of roundwood from Russia before Russia's restriction on log export, experience reduction in imports from Russia by the restriction, then China itself increase production of roundwood and supply to the home market by larger extent than the suppliers in the other countries. In the following empirical sections, we will examine how the supply shock caused by Russia and Myanmar affects the other countries' production and trade flows. The model predicts that the impacts of the supply shock is larger for Russia's (or Myanmar's) direct trade partner, whose market experience reduction in supply, than the other countries. In other words, the reaction of countries who imported roundwood from Russia (Myanmar) increases their production rapidly while the other countries increase production towards such markets by less extent.

@@

In order to apply the causal inference framework, we need to define a treatment in this problem. Here, we define a treatment as a decrease in imports from Russia (Myanmar) due to Russia's (Myanmar's) export restriction policy. If one country imported logs from Russia (Myanmar) before the supply shock, the country would be likely to continue the import from Russia (Myanmar) if Russia (Myanmar) did not implement export restriction policy. On the other hand, if one country did not import any logs from Russia (Myanmar) even before the supply shock, the country would not be likely to import from Russia (Myanmar) even without any restriction policy. Thus, as a proxy of the treatment, we employ a binary variable which indicates the country imported logs from Russia (Myanmar) before the restriction policy. We denote this binary variable with $T_i$, where $T_i$ is 1 if country $i$ imported coniferous roundwood (non-coniferous and non-tropical roundwood) from Russia (Myanmar) one year before the policy intervention, and is 0 otherwise. $T_i = 1$ implies that the country I would be directly exposed to the policy intervention of Russia (Myanmar) in terms of the reduction in imports from Russia (Myanmar). On the other hand, $T_i = 0$ implies that the country would not be directly exposed to the policy. The outcome of interest is country $i$'s production, import, export of roundwoods.\\

Since we have long-term trade panel data before and after the policy intervention, we can implement difference-in-differences approach to estimate the average treatment effects on the treated units (ATT). However, one concern is the heterogeneity in trends between treatment group, that is, those who imported roundwood from Russia (Myanmar), and trend of control group, that is, those who did not import roundwood from Russia (Myanmar). For example, countries who imported logs from Russia (Myanmar) have different locational characteristics from control countries. To address this problem, we use synthetic difference-in-differences method proposed by \cite{xu2017generalized}. \cite{xu2017generalized} integrates synthetic control methods (\cite{abadie2010synthetic}) and linear fixed effects models of DID framework. This method infers counterfactuals for each treated unit with data of control group units by applying synthetic control method. In addition to that, \cite{xu2017generalized} extends the synthetic control approach to a case of multiple treated units.\\

In the estimation, we use country-year-level panel data from 1990 to 2018. We employ two-way fixed effects as additive components of the right-hand side. To obtain information on the uncertainty of the estimates, we calculate standard errors using parametric method with 1000 bootstrap sampling.

@@

>>>>

\begin{abstract}
    Log production is destroying forests around the world and contributing to global warming. To address deforestation, various countries have begun to adopt policies to restrict log exports. However, even if one country restricts log exports, the countries that have been importing logs may increase their log production to compensate for their previous imports. It is also possible that other countries will increase their log exports to the log consuming countries. In this case, one country's log export restrictions could induce deforestation in other countries through trade networks. In this paper, Ifocus on two policies, Russia's log export restrictions in 2007 and Myanmar's log export ban in 2014, to demonstrate how these policies affect the log industry in other countries through trade networks. We find that when one country restricts log exports, log production increases in their previously main export destination. This result suggests that through a network of trade, one country's pro-environmental policies can cause environmental damage in other countries.
\end{abstract}

@@

Using annual trade flow and production data of forestry industries, I employ shift-share design to empirically demonstrate effects of supply shock triggered by the ban of log exports. I regress outcome of each country on how much the country is exposed to the supply shock. The exposure to the shock is measured with interaction of two parts. The first part called ``shift'' is a measure of how much export-restricting country reduces their export to the rest of the world with the restriction. The second part called ``share'' is a measure of how much each country has been dependent on a specific market or industry before the restriction. Combining these two parts, Iobtain measure of how much each country is exposed to the Russia or Myanmar's export restriction policy. By using this shift-share approach, I find that when log export restrictions are imposed in a country, log production increases in the country with the larger exposure to that supply shock, i.e., the country that was the export-restricting country's major export destination. This indicates that a country's log export restrictions contribute to deforestation in its major trading partners. On the other hand, for countries that exported to markets similar to that export-restricting country, there was no significant response in terms of production, export volume, or export value to the export-restriction shock. These results suggest that an pro-environmental policy in one country to protect its own forest has effect to propagate deforestation to their previous trade partners. This implicates that an efficacy of one country's forest protection can be crowded out by the spillover effects. It emphasizes that one government policy to protect its own forest is not sufficient to tackle with global environmental issue.\\

@@

This paper contributes to fill the gap between literature on deforestation and that on pollution heaven hypothesis by empirically shows trade network propagates deforestation with one country's regulation. This study will provide critical evidence in discussing how to solve the issue of deforestation. That is because it is necessary to globally maintain forests and increase how much carbon dioxide can be absorbed in a global scale when Itackle international environment issue such as climate change. Protection of forests in one country at the expense of another country's forest does not contribute to reduction in global carbon dioxide. The results of this paper emphasizes this important implication. \\

@@

In addition to FAOSTAT forestry data, I employ two other data sources. First, I use intra-country bilateral distance data to estimate the impact of distance on trade flows. The distance data are borrowed from the GeoDist database provided by the Centre d'Etudes Prospectives et d'Informations Internationales (CEPII). I use bilateral distance between centers of gravity weighted by the population of each country. Second, Iuse annual GDP data from the World Bank database. I provide descriptive evidence of this dataset in the next section.\\

@@

\subsection{Russia's log export restriction in 2007}
Russia developed the largest coniferous forest in the world, the Siberian ``taiga'', which accounted for half of the world's supply of coniferous wood.  To cope with the deforestation and to promote domestic wood processing industry, Russian government imposed an export tax of 6.5\% in July 2007, rising to 20\% on July 2007 and 25\% in April 2008 on logs exported from Russia. This restriction on log exports was introduced due to the Russian domestic situation. Additionally, as METI points out, the new Russian Forest Code, which was base of these export tax policies, was founded in December 2006. This haste of policy interventions supports my assumption that the policy was exogeneous shock for the rest of the world. \\

@@

\section{A Model of Deforestation Propagation}
Based on the properties of the roundwood trade network, this section constructs a simple model of the roundwood trade, and then presents a hypothesis induced by prediction of the model. The basic framework is quantity competition, what is called, Cournot competition. In usual Cournot setting, firms decide quantity of supply to a market to maximize their profit. On the other hand, I extend this model to quantity competition among firms with assynmetric trade costs. This section describes the Cournot competition model as a game where $n$ countries supply homogeneous roundwood to one market. I introduce a general model at first, and then simplify the model to discuss the implication. \\

I would like to assume that there are n countries which has one market denoted by $M_i$, respectively. Thus, in total, there are $n$ markets $\{ M_1, ..., M_n \}$. In addition to the market, each country has one supplier firm $F_i$, and there are $n$ firms $\{ F_1, ..., F_n \}$ in total. Thus, this is a Cournot model where markets and firms belong to a bipartite graph. Every firm produces an homogeneous good to supply $n$ markets. Each firm choose a vector comsisted of quantity to supply each market, $\mathbf{q}_i = (q_{i1}, ..., q_{in})$ where $q_{ij}$ means quantity that firm $i$ supplies to market $j$. Every market has an identical inverse linear demand function $p_i = D(q_{1i}, ..., q_{ni}) = a_i - \sum_{j=1}^n q_{ji}$. Profit function of each firm is given by $\pi_i (\mathbf{q}_1, ..., \mathbf{q}_n) = \sum_{j = 1}^{n} ((a_j - \sum_{k=1}^n q_{kj}) q_{ij} - c_{i} (\sum_{j = 1}^{n} q_{ij} ) ^ 2 )$. Firms choose their strategy $\mathbf{q}_i$, that is, how much the firm produce and supply to each market, to maximize their profit. As \cite{bimpikis2019cournot} discusses, there is unique Nash equilibrium when this game has symmetric structure, that is, $a_1 = a_2 = ... = a_n = a$ and $c_1 = c_2 = ... = c_n = c$. On the other hand, the uniqueness of the equilibrium and the analytical solution is unknown for assymmetric cases. However, my interest is how assymmetric case where each firm has heterogeneous trade cost to the markets. To be more precise, I would like to discuss how assymmetric trade costs affect firms' decision when one of the firm exit from the markets. Therefore, Ineed to simplify this model from the general model. \\

From now on, Iwill consider a case where there are three countries. We assume that one of the three countries (country $1$) has both a market and a supplier, and the other two countries (country $2$ and country $3$) have only a supplier respectively. We can consider the country with both a market and a supplier as a country which produce roundwood and supply to Chinese market itself. On the other hand, the rest countries are developing countries that have plenty of forests to supply to the large country but that do not have a sufficiently large domestic market, such as Myanmar. Each of the three suppliers (Supplier $i$) chooses quantity $q_i$ to supply the market. The market of country $1$ has a inverse linear demand function
\begin{align}
    p = a - \sum_{i=1}^3 q_i
\end{align}

@@

Thus, Iobtain 
\begin{align}
    q_1^* = \frac{4 a c_{2} c_{3} + 2 a c_{2} + 2 a c_{3} + a}{8 c_{1} c_{2} c_{3} + 8 c_{1} c_{2} + 8 c_{1} c_{3} + 6 c_{1} + 8 c_{2} c_{3} + 6 c_{2} + 6 c_{3} + 4} \\
    q_2^* = \frac{4 a c_{1} c_{3} + 2 a c_{1} + 2 a c_{3} + a}{8 c_{1} c_{2} c_{3} + 8 c_{1} c_{2} + 8 c_{1} c_{3} + 6 c_{1} + 8 c_{2} c_{3} + 6 c_{2} + 6 c_{3} + 4} \\
    q_3^* = \frac{4 a c_{1} c_{2} + 2 a c_{1} + 2 a c_{2} + a}{8 c_{1} c_{2} c_{3} + 8 c_{1} c_{2} + 8 c_{1} c_{3} + 6 c_{1} + 8 c_{2} c_{3} + 6 c_{2} + 6 c_{3} + 4}
\end{align}

@@

Finally, I would like to check how assymmetric trade cost affects each firm's equilibrium strategy (while assuming that production cost is identical among suppliers). As I can infer obviously from the equilibrium strategies, $c_i > c_j > c_k$ implies $q_i^* < q_j^* < q_k^*$ before one firm exits from the market and $c_i > c_j$ implies $q_i^{**} < q_j^{**}$ after one firm exits from the market. It implies that suppliers who need to pay large shipping cost to supply the market produce relatively small quantity. Our main interest is how different trade cost affects suppliers' reaction to the other supplier's exit. The difference in equilibrium supply quantity between before and after Country $3$'s export ban is given by:

@@

Intuitively speaking, Iexpect that $\Delta_i > \Delta_j$ if $c_i < c_j$. Since the form of equilibrium strategies is too complicated to analytical proove this intuitive relationship, I presents results of analytical simulation which support this intuitive property. Figure \ref{fig:cournot_simulation} displays simulation results where $a = 10$ (the intercept of the inverse demand function is $10$) and $c_3 = 1$ (supplier $3$'s cost to produce and supply $q_3$ units is $1$). I calculate $\Delta_1$ and $\Delta_2$ for a total of 121 combinations of $c_1 = 0, 1, ..., 10$ and $c_2 = 0, 1, ..., 10$. Each dot in the figure shows the magnitude relationship between $\Delta_1$ and $\Delta_2$ with its shape and the difference with its color. This figure implies that $\Delta_1 > \Delta_2$ if $c_2 > c_1$, that $\Delta_1 = \Delta_2$ if $c_2 = c_1$, and that that $\Delta_1 < \Delta_2$ if $c_2 < c_1$. In addition to this simulation, I confirm that this result is not sensitive to the value of $a$ and $c_3$. These results support the property of ``$\Delta_i > \Delta_j$ if $c_i < c_j$ ''. \\

@@

Moreover, this property suggests that if supply shock happens to one market, then the supplier with the smallest transportation costs will increase its production and its supply to the market to the greatest extent. In other words, the suppliers located in the same country as the market will increase their production and supply by larger extent than the foreign suppliers. For example, if China, who imported a lot of roundwood from Russia before Russia's restriction on log export, experience reduction in imports from Russia by the restriction, then China itself increase production of roundwood and supply to the home market by larger extent than the suppliers in the other countries. In the following empirical sections, Iwill examine how the supply shock caused by Russia and Myanmar affects the other countries' production and trade flows. The model predicts that the impacts of the supply shock is larger for Russia's (or Myanmar's) direct trade partner, whose market experience reduction in supply, than the other countries. In other words, the reaction of countries who imported roundwood from Russia (Myanmar) increases their production rapidly while the other countries increase production towards such markets by less extent.

@@

In order to apply the causal inference framework, I need to define a treatment in this problem. Here, Idefine a treatment as a decrease in imports from Russia (Myanmar) due to Russia's (Myanmar's) export restriction policy. If one country imported logs from Russia (Myanmar) before the supply shock, the country would be likely to continue the import from Russia (Myanmar) if Russia (Myanmar) did not implement export restriction policy. On the other hand, if one country did not import any logs from Russia (Myanmar) even before the supply shock, the country would not be likely to import from Russia (Myanmar) even without any restriction policy. Thus, as a proxy of the treatment, Iemploy a binary variable which indicates the country imported logs from Russia (Myanmar) before the restriction policy. We denote this binary variable with $T_i$, where $T_i$ is 1 if country $i$ imported coniferous roundwood (non-coniferous and non-tropical roundwood) from Russia (Myanmar) one year before the policy intervention, and is 0 otherwise. $T_i = 1$ implies that the country I would be directly exposed to the policy intervention of Russia (Myanmar) in terms of the reduction in imports from Russia (Myanmar). On the other hand, $T_i = 0$ implies that the country would not be directly exposed to the policy. The outcome of interest is country $i$'s production, import, export of roundwoods.\\

Since Ihave long-term trade panel data before and after the policy intervention, Ican implement difference-in-differences approach to estimate the average treatment effects on the treated units (ATT). However, one concern is the heterogeneity in trends between treatment group, that is, those who imported roundwood from Russia (Myanmar), and trend of control group, that is, those who did not import roundwood from Russia (Myanmar). For example, countries who imported logs from Russia (Myanmar) have different locational characteristics from control countries. To address this problem, I use synthetic difference-in-differences method proposed by \cite{xu2017generalized}. \cite{xu2017generalized} integrates synthetic control methods (\cite{abadie2010synthetic}) and linear fixed effects models of DID framework. This method infers counterfactuals for each treated unit with data of control group units by applying synthetic control method. In addition to that, \cite{xu2017generalized} extends the synthetic control approach to a case of multiple treated units.\\

In the estimation, I use country-year-level panel data from 1990 to 2018. We employ two-way fixed effects as additive components of the right-hand side. To obtain information on the uncertainty of the estimates, I calculate standard errors using parametric method with 1000 bootstrap sampling.

@@

\begin{figure}[H] 
    \centering
    \caption{Impacts of Russia's Export Restriction on Its Trade Partners' Roundwood Import Volume}
    \subfigure[][Coniferous]{\includegraphics*[bb=0 0 650 650, scale=0.15]{"~/OneDrive - The University of Tokyo/deforestation/fig/competitor/Russia/conif_exp_quant.png"}}
    \subfigure[][Non-conif Non-tropical]{\includegraphics*[bb=0 0 650 650, scale=0.15]{"~/OneDrive - The University of Tokyo/deforestation/fig/competitor/Russia/nonconif_nontrop_exp_quant.png"}}
    \subfigure[][Non-conif Tropical]{\includegraphics*[bb=0 0 650 650, scale=0.15]{"~/OneDrive - The University of Tokyo/deforestation/fig/competitor/Russia/nonconif_trop_exp_quant.png"}}
    \caption*{\small{The figure shows impacts of Russia's export restriction policy in 2007 on their trade partners' import volumne of coniferous roundwood (a), non-coniferous non-tropical roundwood (b), and non-coniferous tropical roundwood (c). X axis represents ellapesed time from the policy intervention. Thus, t = 0 means 2007. Y axis is the estimates of ATT. The black lines represent the point estimates and gray shadows represnt 95\% confidence interval.}}
    \label{fig:competitor_exp_Russia}
\end{figure}

\begin{figure}[H] 
    \centering
    \caption{Impacts of Russia's Export Restriction on Its Trade Partners' Roundwood Import Volume}
    \subfigure[][Coniferous]{\includegraphics*[bb=0 0 650 650, scale=0.15]{"~/OneDrive - The University of Tokyo/deforestation/fig/competitor/Russia/conif_Production.png"}}
    \subfigure[][Non-coniferous]{\includegraphics*[bb=0 0 650 650, scale=0.15]{"~/OneDrive - The University of Tokyo/deforestation/fig/competitor/Russia/nonconif_Production.png"}}
    \caption*{\small{The figure shows impacts of Russia's export restriction policy in 2007 on their trade partners' import volumne of coniferous roundwood (a), non-coniferous non-tropical roundwood (b), and non-coniferous tropical roundwood (c). X axis represents ellapesed time from the policy intervention. Thus, t = 0 means 2007. Y axis is the estimates of ATT. The black lines represent the point estimates and gray shadows represnt 95\% confidence interval.}}
    \label{fig:competitor_prod_Russia}
\end{figure}

\begin{figure}[H] 
    \centering
    \caption{Impacts of Russia's Export Restriction on Its Trade Partners' Roundwood Import Volume}
    \subfigure[][Coniferous]{\includegraphics*[bb=0 0 650 650, scale=0.15]{"~/OneDrive - The University of Tokyo/deforestation/fig/competitor/Myanmar/conif_exp_quant.png"}}
    \subfigure[][Non-conif Non-tropical]{\includegraphics*[bb=0 0 650 650, scale=0.15]{"~/OneDrive - The University of Tokyo/deforestation/fig/competitor/Myanmar/nonconif_nontrop_exp_quant.png"}}
    \subfigure[][Non-conif Tropical]{\includegraphics*[bb=0 0 650 650, scale=0.15]{"~/OneDrive - The University of Tokyo/deforestation/fig/competitor/Myanmar/nonconif_trop_exp_quant.png"}}
    \caption*{\small{The figure shows impacts of Russia's export restriction policy in 2007 on their trade partners' import volumne of coniferous roundwood (a), non-coniferous non-tropical roundwood (b), and non-coniferous tropical roundwood (c). X axis represents ellapesed time from the policy intervention. Thus, t = 0 means 2007. Y axis is the estimates of ATT. The black lines represent the point estimates and gray shadows represnt 95\% confidence interval.}}
    \label{fig:competitor_exp_Myanmar}
\end{figure}

\begin{figure}[htbp] 
    \centering
    \caption{Impacts of Russia's Export Restriction on Its Trade Partners' Roundwood Import Volume}
    \subfigure[][Coniferous]{\includegraphics*[bb=0 0 650 650, scale=0.15]{"~/OneDrive - The University of Tokyo/deforestation/fig/competitor/Myanmar/conif_Production.png"}}
    \subfigure[][Non-coniferous]{\includegraphics*[bb=0 0 650 650, scale=0.15]{"~/OneDrive - The University of Tokyo/deforestation/fig/competitor/Myanmar/nonconif_Production.png"}}
    \caption*{\small{The figure shows impacts of Russia's export restriction policy in 2007 on their trade partners' import volumne of coniferous roundwood (a), non-coniferous non-tropical roundwood (b), and non-coniferous tropical roundwood (c). X axis represents ellapesed time from the policy intervention. Thus, t = 0 means 2007. Y axis is the estimates of ATT. The black lines represent the point estimates and gray shadows represnt 95\% confidence interval.}}
    \label{fig:competitor_prod_Myanmar}
\end{figure}
